Tampering Detection In Low-Power \\ Smart Cameras

### 2015-06-22 paper.tex
Modificata frase capitolo 4

The typical figure of merit for assessing detection performance in one-shot monitoring methods are the Receiver-Operating Characteristic (ROC) curves: in our case, these can be computed by varying $\gamma_l$, $\gamma_d$ and $\gamma_g$ in a range of values between $0.1$ and $50$, with step $0.1$. In particular, each point in the ROC curve report a pair of values (1-SPECIFICITY$_\gamma$, RECALL$_\gamma$) defined as
\[1-\text{SPECIFICITY}_\gamma = \frac{\text{FP}_\gamma}{\text{TN}_\gamma+\text{FP}_\gamma}, \ \text{ and } \ \text{RECALL}_\gamma=\frac{\text{TP}_\gamma}{\text{TP}_\gamma+\text{FN}_\gamma}\]
where TP$_\gamma$ represents the number of true positives (tampered frames correctly detected), FP$_\gamma$ of false positives (tampering-free frames detected), TN$_\gamma$ of true negatives (tampering-free frames not detected) and FN$_\gamma$ of false negatives (missed tampered frames), for a given value of $\gamma$.
\vspace{-0.3cm}
\subsubsection{Discussion}
ROC curves in Figure~\ref{fig:ROC}(a)-(b) and the Area Under the Curve (AUC) values reported in the caption indicate that camera displacements can be effectively detected by all the considered methods; the comparison against Voronoi regions suggests that a more substantial advantage is guaranteed when regions fit the scene content. As far as the values of $\Gamma_l$ and $\Gamma_d $ are concerned, the best option is to raise an alert as soon as a single region provides a very clear outlier (i.e., interval \eqref{eq:confidenceRegions} are quite wide). This option is preferable with respect to requiring $K-1$ regions to simultaneously fire an outlier, because it also enable the detection of partial occlusions of the scene. Overall, the ROC curves confirm that $d$ is a far more effective indicator than $l$ in detecting camera displacements.\\
Considering $d$ as indicator, we observe that to limit FPs to $1\%$, Algorithm~\ref{alg:DISPL} have a recall of $99.92\%$, with $\gamma = 15.6$, while considering the whole image solution decreases TPs to $91.67\%$ ($\gamma = 6.5$), as for considering Voronoi's regions ($89.05\%$, $\gamma = 18.64$).
Considering $l$ as indicator, instead, limit FPs to $1\%$ brings a recall of $73.98\%$ when using Algorithm~\ref{alg:DISPL} ($\gamma=5.8$), more than considering the whole image solution ($17.85\%$, $\gamma=3.7$), and Voronoi's regions ($53.02\%$, $\gamma=6$).
Having few false alarms is important in a low-power context, considering the high number of frames that have to be processed. Most importantly, false alerts are halved basically at no computational overhead.\\ %\gi{Aggiornare con i nuovi dati}
%\emph{Considering $d$ as indicator, we observe that to achieve a recall of $98\%$, Algorithm~\ref{alg:DISPL} operates at $0.4\%$ of false alarms, with $\gamma = 24.7$, which is less than one fifth of the whole image solution ($2.2\%$ with $\gamma = 4.6$) and the Voronoi solution ($2.3\%$ with $\gamma = 12.9$).
%On the other side, considering $l$ as indicator, we observe that to achieve a recall of $98\%$, Algorithm~\ref{alg:DISPL} operates at $13\%$ of false alarms, with $\gamma = 2.5$, which is about one sixth of the whole image solution ($75\%$ with $\gamma = 0.1$) and about three fifty than the Voronoi solution ($22\%$ with $\gamma = 1.7 $).
%Having few false alarms is important in a low-power context, considering the high number of frames that have to be processed. Most importantly, false alerts are halved basically at no computational overhead.} \gi{Aggiornare con i nuovi dati}
In contrast, Figure~\ref{fig:ROC}(c) confirms that blurring is more effectively detected by monitoring the whole scene at once. This is probably due to the fact that typically, regions $\{R_k\}$ do not include the most prominent edge of the scene, which are indeed the most informative part to detect blurring. This is the reason why, in Algorithm~\ref{alg:DISPL}, $g$ is monitored on the whole image.%\gi{aggiungere commento su K-1 vornoi che va meglio?}

>>>>

The typical figure of merit for assessing detection performance in one-shot monitoring methods are the Receiver-Operating Characteristic (ROC) curves: in our case, these can be computed by varying $\gamma_l$, $\gamma_d$ and $\gamma_g$ in a range of values between $0.1$ and $50$, with step $0.1$. In particular, each point in the ROC curve report a pair of values (1-SPECIFICITY$_\gamma$, RECALL$_\gamma$) defined as
\[1-\text{SPECIFICITY}_\gamma = \frac{\text{FP}_\gamma}{\text{TN}_\gamma+\text{FP}_\gamma}, \ \text{ and } \ \text{RECALL}_\gamma=\frac{\text{TP}_\gamma}{\text{TP}_\gamma+\text{FN}_\gamma}\]
where TP$_\gamma$ represents the number of true positives (tampered frames correctly detected), FP$_\gamma$ of false positives (tampering-free frames detected), TN$_\gamma$ of true negatives (tampering-free frames not detected) and FN$_\gamma$ of false negatives (missed tampered frames), for a given value of $\gamma$.
\vspace{-0.3cm}
\subsubsection{Discussion}
ROC curves in Figure~\ref{fig:ROC}(a)-(b) and the Area Under the Curve (AUC) values reported in the caption indicate that camera displacements can be effectively detected by all the considered methods; the comparison against Voronoi regions suggests that a more substantial advantage is guaranteed when regions fit the scene content. As far as the values of $\Gamma_l$ and $\Gamma_d $ are concerned, the best option is to raise an alert as soon as a single region provides a very clear outlier (i.e., interval \eqref{eq:confidenceRegions} are quite wide). This option is preferable with respect to requiring $K-1$ regions to simultaneously fire an outlier, because it also enable the detection of partial occlusions of the scene.\\
Considering $d$ as indicator, we observe that to limit FPs to $1\%$, Algorithm~\ref{alg:DISPL} have a recall of $99.92\%$, with $\gamma = 15.6$, while considering the whole image solution decreases TPs to $91.67\%$ ($\gamma = 6.5$), as for considering Voronoi's regions ($89.05\%$, $\gamma = 18.64$).
Considering $l$ as indicator, instead, limit FPs to $1\%$ brings a recall of $73.98\%$ when using Algorithm~\ref{alg:DISPL} ($\gamma=5.8$), more than considering the whole image solution ($17.85\%$, $\gamma=3.7$), and Voronoi's regions ($53.02\%$, $\gamma=6$).
Having few false alarms is important in a low-power context, considering the high number of frames that have to be processed. Most importantly, false alerts are halved basically at no computational overhead.
Finally, ROC curves confirm that $d$ is a far more effective indicator than $l$ in detecting camera displacements.\\ %\gi{Aggiornare con i nuovi dati}
%\emph{Considering $d$ as indicator, we observe that to achieve a recall of $98\%$, Algorithm~\ref{alg:DISPL} operates at $0.4\%$ of false alarms, with $\gamma = 24.7$, which is less than one fifth of the whole image solution ($2.2\%$ with $\gamma = 4.6$) and the Voronoi solution ($2.3\%$ with $\gamma = 12.9$).
%On the other side, considering $l$ as indicator, we observe that to achieve a recall of $98\%$, Algorithm~\ref{alg:DISPL} operates at $13\%$ of false alarms, with $\gamma = 2.5$, which is about one sixth of the whole image solution ($75\%$ with $\gamma = 0.1$) and about three fifty than the Voronoi solution ($22\%$ with $\gamma = 1.7 $).
%Having few false alarms is important in a low-power context, considering the high number of frames that have to be processed. Most importantly, false alerts are halved basically at no computational overhead.} \gi{Aggiornare con i nuovi dati}
In contrast, Figure~\ref{fig:ROC}(c) confirms that blurring is more effectively detected by monitoring the whole scene at once. This is probably due to the fact that typically, regions $\{R_k\}$ do not include the most prominent edge of the scene, which are indeed the most informative part to detect blurring. This is the reason why, in Algorithm~\ref{alg:DISPL}, $g$ is monitored on the whole image.%\gi{aggiungere commento su K-1 vornoi che va meglio?}
